CA Affordabulity

### 2020-09-16 paper.Rmd
update

## Shut-offs
```{r shutoffs}
conn <- ear %>% filter(SectionName=="Connections" & Year==2018)
conn_sfr <- conn %>% filter(QuestionName=="SFR Potable Total" & Year==2018)
conn_mfr <- conn %>% filter(QuestionName=="MFR Potable Total" & Year==2018)
conn_total <- conn %>% filter(QuestionName=="T Potable Total" & Year==2018)

shutoffs <- ear %>% filter(QuestionName=="")
```

>>>>

## Shut-offs
```{r shutoffs}
conn <- ear %>% filter(SectionName=="Connections" & Year==2018)
conn_sfr <- conn %>% filter(QuestionName=="SFR Potable Total" & Year==2018)
conn_mfr <- conn %>% filter(QuestionName=="MFR Potable Total" & Year==2018)
conn_total <- conn %>% filter(QuestionName=="T Potable Total" & Year==2018) %>%rename(connections=QuestionResults) %>% mutate(connections=as.numeric(connections)) %>% select(PWSID,connections) %>% distinct(.keep_all=TRUE)

shutoffs <- ear %>% filter(substr(QuestionName,1,12)=="WR SHUT_OFFS" & Year==2018)

pws_shutoff_collect <- shutoffs %>% filter(QuestionName=="WR SHUT_OFFS Once No Collect" & is.na(QuestionResults))

shutoffs_total <- shutoffs %>%
  filter(QuestionName=="WR SHUT_OFFS Once SF Total" |
           QuestionName=="WR SHUT_OFFS More Than Once SF Total" |
           QuestionName=="WR SHUT_OFFS More Than Once MF Total" |
           QuestionName=="WR SHUT_OFFS Once SF Total") %>%
  group_by(PWSID) %>%
  summarise(shutoffs=sum(as.numeric(QuestionResults),na.rm=TRUE))%>%
  select(PWSID,shutoffs) %>%
  distinct(.keep_all=TRUE) %>% semi_join(pws_shutoff_collect,by="PWSID")

shutoff_comments <- shutoffs %>% filter(QuestionName=="WR SHUT_OFFS Comments")
  re
shutoff_pa<- ear%>%filter(QuestionName=="WR SHUT_OFFS Payment Assistance Total" & Year==2018) %>%distinct(PWSID, QuestionResults) %>% rename(shutoff_pa=QuestionResults) %>% filter(!is.na(shutoff_pa)) %>% mutate(shutoff_pa=as.numeric(shutoff_pa))

conn_shutoff <- left_join(conn_total,shutoffs_total,by="PWSID") %>% mutate(shutoff_rate=shutoffs/connections) %>% filter(connections>0) %>% filter(shutoff_rate<=1)

r_shutoff <- left_join(r,conn_shutoff,by="PWSID") %>% distinct(PWSID,connections,.keep_all=TRUE) %>%
ggplot(filter(r_shutoff), aes(x=size_cat, y=shutoff_rate, colour=Ownership)) +
  geom_boxplot()

lm()
